Through the Eyes of the Teacher - Multimodal Exploration of Expertise Differences in the Perception of Classroom Disruptions in a Laboratory Study

### 2025-02-18 02_paper/02_study/02_expertise_paper/expertise_2025_01_23_MK.Rmd
xxxx

>>>>

### Correlation table for all participants

# Define relevant columns for correlation analysis
correlation_columns <- c(
  "GRI", 
  "Stud_number_fixation_min",
  "log_Disrup_time_fixation_sec",
  "Disruption_Rating", 
  "Confidence_Rating", 
  "SJT_All", 
  "Self_Eval_Overall"
)

# Drop rows with missing values
df_correlation_all <- df_merge %>%
  select(all_of(correlation_columns)) %>%
  drop_na()

# Compute Pearson correlation matrix
cor_results_all <- rcorr(as.matrix(df_correlation_all))

# Extract correlation coefficients and p-values
cor_matrix_all <- cor_results_all$r
p_matrix_all <- cor_results_all$P

# Convert correlation and p-value matrices into a tidy format
correlation_pvalues_all <- as.data.frame(as.table(cor_matrix_all)) %>%
  rename(Variable1 = Var1, Variable2 = Var2, Correlation = Freq) %>%
  left_join(
    as.data.frame(as.table(p_matrix_all)) %>%
      rename(Variable1 = Var1, Variable2 = Var2, P_value = Freq),
    by = c("Variable1", "Variable2")
  ) %>%
  filter(Variable1 != Variable2) %>%
  mutate(
    Correlation = round(Correlation, 2),
    P_value = round(P_value, 3),
    APA_Format = paste0(Correlation, ifelse(P_value < 0.05, "*", ""))
  )

# Reshape into a correlation table format
correlation_table_all <- correlation_pvalues_all %>%
  select(Variable1, Variable2, APA_Format) %>%
  pivot_wider(names_from = Variable2, values_from = APA_Format)

# Ensure Variable1 is a factor to maintain order
correlation_table_all$Variable1 <- factor(correlation_table_all$Variable1, levels = unique(correlation_table_all$Variable1))

# Create APA-styled table
cor_flextable_all <- correlation_table_all %>%
  flextable() %>%
  theme_booktabs() %>%
  autofit() %>%
  set_caption("Table: Correlation Table for All Participants")

# Print the table
cor_flextable_all
